Supplementary Information

### 2020-10-08 writing/transect_paper.Rmd
switch to xelatex, as required by thesis printing.

---
title: "Long- and short-read metabarcoding technologies reveal similar spatio-temporal structures in fungal communities"
author: 
  - Brendan Furneaux^1,\*^,
  - Mohammad Bahram^2,3^,
  - Anna Rosling^4^,
  - Nourou S. Yorou^5^,
  - Martin Ryberg^1^
date: |
      | ^1^Program in Systematic Biology,
        Department of Organismal Biology,
        Uppsala University,
        Uppsala, Sweden
      | ^2^Department of Ecology,
        Swedish University of Agricultural Sciences,
        Uppsala, Sweden
      | ^3^Institute of Ecology and Earth Sciences,
        University of Tartu,
        Tartu, Estonia
      | ^4^Program in Evolutionary Biology,
        Department of Ecology and Genetics,
        Uppsala University,
        Uppsala, Sweden
      | ^5^Research Unit in Tropical Mycology and Plant-Fungi Interactions,
        LEB,
        University of Parakou,
        Parakou, Benin
      | ^\*^Corresponding author, `brendan.furneaux@ebc.uu.se`
bibliography:
  - "all.bib"
  - "R.bib"
biblio-style: apa
always_allow_html: true
output:
  bookdown::pdf_document2:
    template: bare_template.tex
    fig_crop: true
    keep_tex: true
    toc: false
    latex_engine: lualatex
    includes:
      in_header: preamble.tex
    citation_package: biblatex
    suppress-bibliography: true
  bookdown::word_document2: 
    keep_md: yes
fontsize: 12pt
geometry: ["left=2.5cm", "right=2.5cm", "top=3cm", "bottom=3cm"]
graphics: yes
---

>>>>

---
title: "Long- and short-read metabarcoding technologies reveal similar spatio-temporal structures in fungal communities"
author: 
  - Brendan Furneaux^1,\*^,
  - Mohammad Bahram^2,3^,
  - Anna Rosling^4^,
  - Nourou S. Yorou^5^,
  - Martin Ryberg^1^
date: |
      | ^1^Program in Systematic Biology,
        Department of Organismal Biology,
        Uppsala University,
        Uppsala, Sweden
      | ^2^Department of Ecology,
        Swedish University of Agricultural Sciences,
        Uppsala, Sweden
      | ^3^Institute of Ecology and Earth Sciences,
        University of Tartu,
        Tartu, Estonia
      | ^4^Program in Evolutionary Biology,
        Department of Ecology and Genetics,
        Uppsala University,
        Uppsala, Sweden
      | ^5^Research Unit in Tropical Mycology and Plant-Fungi Interactions,
        LEB,
        University of Parakou,
        Parakou, Benin
      | ^\*^Corresponding author, `brendan.furneaux@ebc.uu.se`
bibliography:
  - "all.bib"
  - "R.bib"
biblio-style: apa
always_allow_html: true
output:
  bookdown::pdf_document2:
    template: bare_template.tex
    fig_crop: true
    keep_tex: true
    toc: false
    latex_engine: xelatex
    includes:
      in_header: preamble.tex
    citation_package: biblatex
    suppress-bibliography: true
  bookdown::word_document2: 
    keep_md: yes
fontsize: 12pt
geometry: ["left=2.5cm", "right=2.5cm", "top=3cm", "bottom=3cm"]
graphics: yes
---

### 2020-10-08 writing/transect_supplement.Rmd
switch to xelatex, as required by thesis printing.

---
title: 
  - "Supplementary Information for:"
  - "Long- and short-read metabarcoding technologies reveal similar spatio-temporal structures in fungal communities"
author: 
  - Brendan Furneaux^1^,
  - Mohammad Bahram^2,3^,
  - Anna Rosling^4^,
  - Nourou S. Yorou^5^,
  - Martin Ryberg^1^
  - ^1^Program in Systematic Biology,
    Department of Organismal Biology,
    Uppsala University,
  - Uppsala, Sweden
  - ^2^Department of Ecology,
    Swedish University of Agricultural Sciences,
    Uppsala, Sweden
  - ^3^Institute of Ecology and Earth Sciences,
    University of Tartu,
    Tartu, Estonia
  - ^4^Program in Evolutionary Biology,
    Department of Ecology and Genetics,
    Uppsala University,
  - Uppsala, Sweden
  - ^5^Research Unit in Tropical Mycology and Plant-Fungi Interactions,
    LEB,
  - University of Parakou,
    Parakou, Benin
always_allow_html: true
output:
  bookdown::pdf_document2:
    fig_crop: yes
    keep_tex: yes
    toc: false
    latex_engine: lualatex
    includes:
      in_header: preamble_supplement.tex
    citation_package: biblatex
    suppress-bibliography: true
    fontsize: 12pt
    geometry: left=2.5cm, right=2.5cm, top=3cm, bottom=3cm
---

>>>>

---
title: 
  - "Supplementary Information for:"
  - "Long- and short-read metabarcoding technologies reveal similar spatio-temporal structures in fungal communities"
author: 
  - Brendan Furneaux^1^,
  - Mohammad Bahram^2,3^,
  - Anna Rosling^4^,
  - Nourou S. Yorou^5^,
  - Martin Ryberg^1^
  - ^1^Program in Systematic Biology,
    Department of Organismal Biology,
    Uppsala University,
  - Uppsala, Sweden
  - ^2^Department of Ecology,
    Swedish University of Agricultural Sciences,
    Uppsala, Sweden
  - ^3^Institute of Ecology and Earth Sciences,
    University of Tartu,
    Tartu, Estonia
  - ^4^Program in Evolutionary Biology,
    Department of Ecology and Genetics,
    Uppsala University,
  - Uppsala, Sweden
  - ^5^Research Unit in Tropical Mycology and Plant-Fungi Interactions,
    LEB,
  - University of Parakou,
    Parakou, Benin
always_allow_html: true
output:
  bookdown::pdf_document2:
    fig_crop: yes
    keep_tex: yes
    toc: false
    latex_engine: xelatex
    includes:
      in_header: preamble_supplement.tex
    citation_package: biblatex
    suppress-bibliography: true
    fontsize: 12pt
    geometry: left=2.5cm, right=2.5cm, top=3cm, bottom=3cm
---
